Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-02-08 paper/icmssp2019-sigconf.tex
Renamed main tex file
Started edits

\numberofauthors{2}
\author{
\alignauthor Aldrich Ellis C. Asuncion\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Ave., Loyola Heights}\\
\affaddr{Quezon City, Philippines 1108}\\
\email{aldrich.asuncion@obf.ateneo.edu}
\alignauthor Brian Christopher T. Guadalupe\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Ave., Loyola Heights}\\
\affaddr{Quezon City, Philippines 1108}\\
\email{brian.guadalupe@obf.ateneo.edu}
}

\maketitle
% The default list of authors is too long for headers.
% \renewcommand{\shorttitle}{Impl. and Analysis of Homomorphic Facial Image Encryption and Manipulation}
% \renewcommand{\shortauthors}{A. Asuncion and B. Guadalupe}

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy, In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10002978.10002979.10002981.10011745</concept_id>
  <concept_desc>Security and privacy~Public key encryption</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003018.10003020</concept_id>
  <concept_desc>Security and privacy~Management and querying of encrypted data</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003029.10011150</concept_id>
  <concept_desc>Security and privacy~Privacy protections</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010371.10010382.10010383</concept_id>
  <concept_desc>Computing methodologies~Image processing</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002950.10003714.10003736.10003737</concept_id>
  <concept_desc>Mathematics of computing~Approximation</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10002950.10003714.10003740</concept_id>
  <concept_desc>Mathematics of computing~Quadrature</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Public key encryption}
\ccsdesc[300]{Security and privacy~Management and querying of encrypted data}
\ccsdesc[300]{Security and privacy~Privacy protections}
\ccsdesc[500]{Computing methodologies~Image processing}
\ccsdesc[300]{Mathematics of computing~Approximation}
\ccsdesc[100]{Mathematics of computing~Quadrature}

\printccsdesc
\keywords{cryptography; homomorphic encryption; data privacy; image processing; intensity transformation; facial recognition; numerical approximations}

@@

% \begin{acks}
\section{Acknowledgments}
We would like to thank our adviser Dr. William Emmanuel S. Yu for his guidance and constant feedback, and our panelists Dr. Andrei D. Coronel and Dr. Mari-jo P. Ruiz for lending their expertise and for giving their invaluable comments and insights.
Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
% \end{acks}

@@

\appendix
\input{appendix}
\balancecolumns

>>>>

\numberofauthors{2}
\author{
\alignauthor Aldrich Ellis C. Asuncion\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Avenue, Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{aldrich.asuncion@obf.ateneo.edu}
\alignauthor Brian Christopher T. Guadalupe\\
\affaddr{Ateneo de Manila University}\\
\affaddr{Katipunan Avenue, Loyola Heights}\\
\affaddr{Quezon City, Philippines}\\
\email{brian.guadalupe@obf.ateneo.edu}
}

\maketitle

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), Dasgupta--Pal, and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and Dasgupta--Pal cryptosystems are comparable in accuracy and may be used to approximate a logarithm transformation, but the Dasgupta--Pal cryptosystem is significantly slower.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10002978.10002979.10002981.10011745</concept_id>
  <concept_desc>Security and privacy~Public key encryption</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003018.10003020</concept_id>
  <concept_desc>Security and privacy~Management and querying of encrypted data</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10002978.10003029.10011150</concept_id>
  <concept_desc>Security and privacy~Privacy protections</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010371.10010382.10010383</concept_id>
  <concept_desc>Computing methodologies~Image processing</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Public key encryption}
\ccsdesc[300]{Security and privacy~Management and querying of encrypted data}
\ccsdesc[300]{Security and privacy~Privacy protections}
\ccsdesc[500]{Computing methodologies~Image processing}

\printccsdesc
\keywords{cryptography; homomorphic encryption; data privacy; image processing; intensity transformation; facial recognition}

@@

% \begin{acks}
\section{Acknowledgments}
% We would like to thank our adviser Dr. William Emmanuel S. Yu for his guidance and constant feedback, and 
We would like to thank our panelists Dr. Andrei D. Coronel and Dr. Mari-Jo P. Ruiz for lending their expertise and for giving their invaluable comments and insights.
Due acknowlegement is also given to the University of Essex for making the \texttt{faces94} dataset publicly available for research purposes.
% \end{acks}

@@

% \appendix
% \input{appendix}
% \balancecolumns

### 2019-02-08 paper/paper-conf.tex
Started edits

\subsection{Research Questions}
By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?

More specifically, our research will address the following sub-questions:
\begin{enumerate}
	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
\end{enumerate}

@@

There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

@@

\subsubsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

\paragraph{Key Generation}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

\paragraph{Encryption and Decryption}
The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2},
\end{align*}
where $r$ is a random non-negative integer less than $n^2$.

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

@@

\paragraph{Key Generation}
We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
Let $p,q$ be primes such that
we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
We denote $n = pq$.
We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.

The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.

The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.

\paragraph{Encryption and Decryption}
To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
\begin{align*}
  E(m) = g^m \cdot h^r \mod{n},
\end{align*}
where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.

To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
\begin{align*}
	c^{v_pv_q} \bmod n
	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
	&= (g^{v_pv_q})^m \bmod n
\end{align*}
Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$. A lookup table can thus be generated privately to successfully recover $m$.

@@

\subsubsection{Secure Exponentiation and Multiplication Protocols}
\label{ssec:exponentiationprotocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
\end{itemize}

We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
\begin{itemize}
	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
	\item Alice sends $E((x+y)^2)$ to Bob.
	\item Bob then computes
	\begin{align*}
		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
		&= E(2xy)
	\end{align*}
	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$. Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
\end{itemize}

@@

In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set. The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.

The average of the training images, denoted as $\Psi$, is 
\begin{equation}
	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
\end{equation}

The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
\begin{equation}
	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
\end{equation}
where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.

Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image. On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set. Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.

Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$. This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}. Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.

We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$. This set is now the \textit{face space}. Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.

To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance. Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.

Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
\newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
\begin{equation}
	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
\end{equation}

@@

\subsection{Secure Computation with Real Numbers}
We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively. We define the secure real number operations as follows:
\begin{description}
  \item[Addition.]
    To compute $E(c)=E(a+b)$ we compute
    \begin{align*}
      E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
      E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
    \end{align*}
  \item[Scalar multiplication.]
    To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
    \begin{align*}
      E(m_c) &= m_a \otimes E(m_b)\\
      e_c &= e_a + e_b
    \end{align*}
\end{description}

>>>>

% \subsection{Research Questions}
% By implementing homomorphic cryptosystems and creating a library so they can be easily used, we aim to address our main research question: What is the best method for facial image data to be encrypted and manipulated for practical applications?

% More specifically, our research will address the following sub-questions:
% \begin{enumerate}
% 	\item Which homomorphic cryptosystems admit more image processing operations? How can existing homomorphic cryptosystems be modified to admit more image processing operations?
% 	\item Which homomorphic cryptosystems are the most time-efficient and the most accurate in applying image processing operations?
% 	\item Which homomorphic cryptosystems best preserve image quality in applying image processing operations?
% \end{enumerate}

@@

% There are two kinds of cryptosystems, \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, symmetric-key cryptosystems must be implemented with a secure key exchange protocol, so that both the sender and receiver have access to the same key. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

% On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared publicly, while the decryption key (also called the \textit{private key}) is kept secret. Since the public key and private keys are different, there is no need to agree upon secure key exchange protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, for example, the RSA cryptosystem depends on the difficulty of big integer factorization~\cite{rivest_method_1978}, while the ElGamal cryptosystem depends on the difficulty of the discrete logarithm problem~\cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem in which operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\boxdot$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively~\cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies~\cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \boxdot \mathcal{E}_k \left(p_2\right) \right).
\end{equation}

In other words, a homomorphic cryptosystem preserves the operations that can be done with the plaintext without requiring an intermediary step of decrypting the ciphertext beforehand. It is important to note that the operations $\boxplus$ and $\boxdot$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

@@

\subsubsection{The Paillier Cryptosystem}
The Paillier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Paillier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. 
% We now state the encryption and decryption algorithms of the Paillier cryptosystem and its homomorphic properties.

% \paragraph{Key Generation}
% We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
% We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
% Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
% We denote the public key as $(g,n)$ and the private key $(p,q)$.

% \paragraph{Encryption and Decryption}
% The encryption function to encrypt a plaintext $m \in \mathbb{Z}_n$ given a public key $(g,n)$ is defined as
% \begin{align*}
%   E(m) = g^m \cdot r^n \mod{n^2},
% \end{align*}
% where $r$ is a random non-negative integer less than $n^2$.

% The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
% \begin{align*}
%   D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
% \end{align*}

@@

% \paragraph{Key Generation}
% We denote $k,t,\ell$ as security parameters of the scheme, where $k>t>\ell$.
% Let $p,q$ be primes such that
% we can choose two $t$-bit primes $v_p$ and $v_q$ such that $v_p | (p-1)$ and $v_q | (q-1)$, and a small prime $u$ such that $u | (p-1)$ and $u | (q-1)$.
% We denote $n = pq$.
% We choose $g$ to be an integer of order $uv_pv_q$ and $h$ to be of order $v_pv_q$.

% The DGK cryptosystem encrypts plaintexts in $\mathbb{Z}_u$ to ciphertexts in $\mathbb{Z}_n^\ast$.

% The public key is $(n,g,h,u)$ and the private key is $(p,q,v_p,v_q)$.

% \paragraph{Encryption and Decryption}
% To encrypt a message $m \in \mathbb{Z}_u$, the encryption function is defined as:
% \begin{align*}
%   E(m) = g^m \cdot h^r \mod{n},
% \end{align*}
% where $r$ is a random integer in $\mathbb{Z}_n$ which is longer than $2t$ bits.

% To decrypt a ciphertext $c \in \mathbb{Z}_n^\ast$, decryption is achieved by first computing $c^{v_pv_q}$.
% \begin{align*}
% 	c^{v_pv_q} \bmod n
% 	&= (g^m \cdot h^r)^{v_pv_q} \bmod n\\
% 	&= (g^{v_pv_q})^m \bmod n
% \end{align*}
% Since $(g^{v_pv_q})^m$ has order $u$, there is a one-to-one correspondence between plaintexts in $\mathbb{Z}_u$ and  $(g^{v_pv_q})^m$. A lookup table can thus be generated privately to successfully recover $m$.

@@

\subsubsection{Secure Exponentiation and Multiplication Protocols}
\label{ssec:exponentiationprotocol}
[TO-DO: This is further explained in another paper.]
% In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

% The following protocols apply to both the Paillier and DGK cryptosystems, as they share similar homomorphisms. We first present a secure squaring protocol.

% Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
% \begin{itemize}
% 	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
% 	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
% 	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
% 	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
% \end{itemize}

% We can use the secure squaring protocol to arrive at a secure multiplication protocol, which then allows for the evaluation of polynomials.
% Suppose Alice encrypts integers $x$ and $y$, and Bob has $E(x), E(y)$ and wants to obtain $E(xy)$.
% \begin{itemize}
% 	\item Bob acquires $E(x^2), E(y^2)$ using the secure squaring protocol.
% 	\item Bob sends $E(x+y)$ to Alice, who decrypts the ciphertext to obtain $x+y$.
% 	\item Alice sends $E((x+y)^2)$ to Bob.
% 	\item Bob then computes
% 	\begin{align*}
% 		E((x+y)^2)E(x^2)^{-1}E(y^2)^{-1} &= E((x+y)^2 - x^2 - y^2)\\
% 		&= E(2xy)
% 	\end{align*}
% 	\item Bob can then recover $E(xy)$ by calcuating for the multiplicative inverse of 2 using the Euclidean algorithm, and calculating $2^{-1}E(xy)$. Such an inverse exists since the modulus is either a prime (in the DGK cryptosystem) or a product of primes greater than 2 (in the Paillier cryptosystem).
% \end{itemize}

@@

% In the enrollment process, $M$ face images $\Theta_1, \ldots, \Theta_M$, each of size $p \times q$, are taken in to comprise the initial training set. The training images can be represented as vectors of length $N = pq$, where each row of an image is concatenated together.

% The average of the training images, denoted as $\Psi$, is 
% \begin{equation}
% 	\Psi = \frac{1}{M} \sum_{i=1}^{M} \Theta_i
% \end{equation}

% The \textit{difference vectors} are then computed as $\Phi_i = \Theta_i - \Psi$. PCA is applied on the covariance matrix of the vectors
% \begin{equation}
% 	\mathbf{C} = \frac{1}{M} \sum_{i=1}^M \Phi_i \Phi_i^\top = \frac{1}{M} \mathbf{A}\mathbf{A}^\top,
% \end{equation}
% where $\mathbf{A}$ is an $N \times M$ matrix defined by $\left[\Theta_1 \quad \Theta_2 \quad \cdots \quad \Theta_M\right]$, in order to determine the orthonormal eigenvectors \cite{hutchison_privacy-preserving_2009}.

% Directly computing the covariance matrix and then applying PCA will become inefficient for large sizes of $\mathbf{A}$, since computing for $\mathbf{A}\mathbf{A}^\top$ results in an $N \times N$ matrix, which can get drastically large because it is dependent on the size of the image. On the other hand, computing for $\mathbf{A}^\top\mathbf{A}$ only results in an $M \times M$ matrix, which is much smaller than the previous one because it is just dependent on the number of face images in the training set. Now, we can apply PCA to $\mathbf{A}^\top\mathbf{A}$ along with some post-processing to obtain the eigenvectors \cite{hutchison_privacy-preserving_2009}.

% Instead of getting the eigendecomposition of the covariance matrix by explicitly computing the eigenvalues and eigenvectors of $\mathbf{C}$, we can also apply \textit{singular value decomposition} (SVD) on the matrix $\Phi^\top$. This is because SVD works through a divide-and-conquer method which results in greater numerical stability, while eigendecomposition simply uses the traditional QR factorization \cite{nakatsukasa_stable_2013, gu_divide-and-conquer_1995}. Upon applying SVD, we now get the eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_M$ and their corresponding eigenvalues $\lambda_1, \ldots, \lambda_M$.

% We choose $K$ eigenvectors $\mathbf{u}_1, \ldots, \mathbf{u}_K$ such that it comprises a set associated with the $K$ largest eigenvalues, where $K$ is much smaller than $M$. This set is now the \textit{face space}. Then, the images $\Theta_1, \ldots, \Theta_K$ are projected onto the face space spanned by the eigenfaces to determine the weight vectors $\Omega_1, \ldots, \Omega_K$.

% To perform the recognition process, the algorithm projects the input image $\Gamma$ onto the face space, and then comparing the projected image $\bar{\Omega} = \mathbf{u}_i\left(\Gamma - \Psi\right)$ with each eigenface in the face space using a metric such as the Euclidean distance. Thus it is computed as $d_i = \left\lVert \Omega_i -\bar{\Omega} \right\rVert$ for all $i=1,\ldots,K$, where $\left\lVert \cdot \right\rVert$ denotes the Euclidean norm.

% Then, a match can be reported if the smallest possible distance is smaller than the given threshold value $T$. 
% \newcommand{\argmin}{\mathop{\mathrm{arg\,min}}}  
% \begin{equation}
% 	\text{ID} = \begin{cases}\argmin_i d_i & \text{if } \min_i d_i \le T \\\emptyset & \text {otherwise}\end{cases}
% \end{equation}

@@

\subsection{Secure Computation with Real Numbers}
[TO-DO: This is further explained in another paper.]
% We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
% The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
% This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

% We represent a floating-point (FP) number as a pair of two integers $(m,e)$ representing the mantissa and exponent of the FP number with respect to a base $b$. The mantissa $m$ is encrypted, while the exponent $e$ is unencrypted.
% Let $a,b,c$ be FP numbers represented by the pairs $(m_a,e_a),(m_b,e_b),(m_c,e_c)$ respectively. Let $\oplus,\otimes$ represent the homomorphic operations which correspond to the addition and multiplication, respectively. We define the secure real number operations as follows:
% \begin{description}
%   \item[Addition.]
%     To compute $E(c)=E(a+b)$ we compute
%     \begin{align*}
%       E(m_c) &= E(m_1) \oplus (b^{e_b-e_a} \otimes E(m_b)), e_c = e_a & \text{ if } e_a \leq e_b \\
%       E(m_c) &= E(m_b) \oplus (b^{e_a-e_b} \otimes E(m_a)), e_c = e_b & \text{ if } e_a > e_b
%     \end{align*}
%   \item[Scalar multiplication.]
%     To compute $E(c) = E(ab)$, where $a$ and $E(b)$ are known (i.e. $m_a$ is not encrypted), we compute
%     \begin{align*}
%       E(m_c) &= m_a \otimes E(m_b)\\
%       e_c &= e_a + e_b
%     \end{align*}
% \end{description}
